Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-17 PaperDraft.Rmd

>>>>

As the model is much more complex than the one in the Thompson et al. paper, we
are unable to derive an analytic expression to compute the posterior. Instead,
we use `rstan` to run $4$ chains of MCMC for $2000$ iterations each.

### Using OLS and EpiEstim to check results

[TK: @Ben mention the OLS against EpiEstim ]
